
1. Your reasoning for choosing the things that you did to measure what makes a basketball team good.
The very first thing that I put in my model is team and opponent field goal percentage. If teams don't make shots, they won't be good. I also chose to include team ppp. I had opponent ppp in there, but it was causing me a lot of issues, so I got rid of it and it helped a lot. Not sure why. I have offensive rebounds (a similar thing happened with defensive rebounds as did with opponent ppp. There were a lot of outliers and I had a ton of 12-13 seeds in the final four) for both team and opponent -- if you have multiple chances per possession to shoot, you'll score more. I also had fouls for both. Don't get in foul trouble and make sure that the other team does (thanks, Jeff Greisch). I also had team and opponent median player value to try to account for some strength of schedule.

2. The implementation of your feature engineering (the stuff that feeds modelgames).
In the notebook

3. The justification of your model choice.
I chose to use light GBM because it gave me decent accuracy and was way faster than SVM. I decided SVM wasn't worth it for the <1%.

4. The implemetation of your model and predictions.
In the notebook

----- FEATURE ENGINEERING -----

```{r}
library(tidyverse)
library(hoopR)
library(zoo)
library(tidymodels)
library(bonsai)

games <- load_mbb_team_box(2015:2023) %>% filter(game_date < as.Date("2023-03-14"))
schedule <- load_mbb_schedule(2015:2023) %>% filter(game_date < as.Date("2023-03-14"))
boxscore <- load_mbb_team_box(2015:2023) %>% filter(game_date < as.Date("2023-03-14"))
players <- load_mbb_player_box(2015:2023) %>% filter(game_date < as.Date("2023-03-14"))

gameswithpossessions <- games %>% 
  mutate(
    possessions = round(field_goals_attempted - offensive_rebounds + turnovers + (.475 * free_throws_attempted), digits=0),
    points_per_100 = (team_score/possessions)*100
  ) %>% 
  filter(possessions <= 90 & possessions >= 53)

playervalues <- players %>% 
  filter(minutes >0) %>% 
  mutate(
    value = points + rebounds + assists + steals + blocks - turnovers - (field_goals_attempted - field_goals_made) - (free_throws_attempted - free_throws_made)
  ) %>% 
  group_by(team_short_display_name) %>% 
  summarize(
    games = n(),
    team_player_average_value = mean(value),
    standard_dev = sd(value),
    team_player_median_value = median(value)
  ) 

gameswithpossessions <- gameswithpossessions %>% inner_join(playervalues)

rollingteamstats <- gameswithpossessions %>% 
  arrange(game_date) %>%
  group_by(team_short_display_name, season) %>%
  mutate(
    team_rolling_ppp = rollmean(lag(points_per_100, n=1), k=5, align="right", fill=NA),
    team_rolling_median_value = rollmean(lag(team_player_median_value, n=1), k=5, align="right", fill=NA),
    team_rolling_fgpct = rollmean(lag(field_goal_pct, n=1), k=5, align="right", fill=NA),
    team_cumulative_ppp = lag(cummean(points_per_100), n=1),
    team_rolling_fouls = rollmean(lag(fouls, n=1), k=5, align="right", fill=NA),
    team_rolling_turnovers = rollmean(lag(turnovers, n=1), k=5, align="right", fill=NA),
    team_cumulative_player_value = lag(cummean(team_player_median_value), n=1)
    #team_rolling_offensive_rebound_factor = rollmean(lag(team_offensive_rebound_factor, n=1), k=5, align="right", fill=NA)
    ) %>% 
ungroup()

team_side <- rollingteamstats %>%
  select(
    game_id,
    team_id, 
    team_short_display_name, 
    opponent_team_id,
    game_date, 
    season, 
    team_score, 
    team_rolling_fouls,
    team_rolling_ppp,
    team_rolling_median_value,
    team_rolling_fgpct,
    team_cumulative_player_value,
    team_cumulative_ppp,
    offensive_rebounds,
    defensive_rebounds,
    team_rolling_turnovers
    ) %>% 
  rename(
    team_offensive_rebounds = offensive_rebounds,
    team_defensive_rebounds = defensive_rebounds
  ) %>% 
  na.omit() 

opponent_side <- team_side %>%
  select(-opponent_team_id) %>% 
  rename(
    opponent_team_id = team_id,
    opponent_short_display_name = team_short_display_name,
    opponent_score = team_score,
    opponent_rolling_ppp = team_rolling_ppp,
    opponent_rolling_median_value = team_rolling_median_value,
    opponent_rolling_fgpct = team_rolling_fgpct,
    opponent_cumulative_player_value = team_cumulative_player_value,
    opponent_cumulative_ppp = team_cumulative_ppp,
    opponent_offensive_rebounds = team_offensive_rebounds,
    opponent_defensive_rebounds = team_defensive_rebounds,
    opponent_rolling_fouls = team_rolling_fouls,
    opponent_rolling_turnovers = team_rolling_turnovers
  ) 

gameswithsides <- team_side %>% inner_join(opponent_side)

gameswithsides <- gameswithsides %>% mutate(
  team_result = as.factor(case_when(
    team_score > opponent_score ~ "W",
    opponent_score > team_score ~ "L"
  )),
team_offensive_rebound_factor = team_offensive_rebounds / (team_offensive_rebounds + opponent_defensive_rebounds),
opponent_offensive_rebound_factor = opponent_offensive_rebounds / (opponent_offensive_rebounds + team_defensive_rebounds),
team_rolling_offensive_rebound_factor = rollmean(lag(team_offensive_rebound_factor, n=1), k=10, align="right", fill=NA),
opponent_rolling_offensive_rebound_factor = rollmean(lag(opponent_offensive_rebound_factor, n=1), k=10, align="right", fill=NA
),
team_defensive_rebound_factor = team_defensive_rebounds / (team_defensive_rebounds + opponent_offensive_rebounds),
opponent_defensive_rebound_factor = opponent_defensive_rebounds / (opponent_defensive_rebounds + team_offensive_rebounds),
team_rolling_defensive_rebound_factor = rollmean(lag(team_defensive_rebound_factor, n=1), k=10, align="right", fill=NA),
opponent_rolling_defensive_rebound_factor = rollmean(lag(opponent_defensive_rebound_factor, n=1), k=10, align="right", fill=NA
) ) %>% 
na.omit()

levels(gameswithsides$team_result)

gameswithsides$team_result <- relevel(gameswithsides$team_result, ref="W")

levels(gameswithsides$team_result)

modelgames <- gameswithsides %>% 
  select(
    game_id, 
    game_date, 
    team_short_display_name, 
    opponent_short_display_name, 
    season, 
    team_rolling_ppp, 
   # opponent_rolling_ppp, 
    team_result,
    team_rolling_median_value,
    opponent_rolling_median_value,
    team_rolling_fgpct,
    opponent_rolling_fgpct,
    #team_cumulative_player_value,
    team_cumulative_ppp,
    #opponent_cumulative_player_value,
    #opponent_cumulative_ppp,
    team_rolling_offensive_rebound_factor,
    opponent_rolling_offensive_rebound_factor,
    #team_rolling_defensive_rebound_factor,
    #opponent_rolling_defensive_rebound_factor,
    team_rolling_fouls,
    opponent_rolling_fouls,
    #team_rolling_turnovers,
    #opponent_rolling_turnovers
    ) %>% na.omit()

log_split <- initial_split(modelgames, prop = .8)
log_train <- training(log_split)
log_test <- testing(log_split)

log_recipe <- 
  recipe(team_result ~ ., data = log_train) %>% 
  update_role(game_id, game_date, team_short_display_name, opponent_short_display_name, season, new_role = "ID")
summary(log_recipe)

lightgbm_mod <- 
  boost_tree() %>% 
  set_engine("lightgbm") %>% 
  set_mode(mode = "classification") 

lightgbm_workflow <- 
  workflow() %>% 
  add_model(lightgbm_mod) %>% 
  add_recipe(log_recipe)

lightgbm_fit <- 
  lightgbm_workflow %>% 
  fit(data = log_train)

lightgbmtestpredict <- lightgbm_fit %>% predict(new_data = log_test) %>%
  bind_cols(log_test) 

lightgbmtestpredict <- lightgbm_fit %>% predict(new_data = log_test, type="prob") %>%
  bind_cols(lightgbmtestpredict)

metrics(lightgbmtestpredict, team_result, .pred_class)
```


---- FUTURE FEATURE ENGINEERING ----

```{r}
rollingteamstats <- gameswithpossessions %>% 
  arrange(game_date) %>%
  group_by(team_short_display_name, season) %>%
  mutate(
    team_rolling_ppp = rollmean(points_per_100, k=5, align="right", fill=NA),
    team_rolling_median_value = rollmean(team_player_median_value, k=5, align="right", fill=NA),
    team_rolling_fgpct = rollmean(field_goal_pct, k=5, align="right", fill=NA),
    team_cumulative_ppp = cummean(points_per_100),
    team_rolling_fouls = rollmean(fouls, k=5, align="right", fill=NA),
    team_rolling_turnovers = rollmean(turnovers, k=5, align="right", fill=NA),
    #team_cumulative_player_value = cummean(team_median_player_value),
    #team_rolling_offensive_rebound_factor = rollmean(lag(team_offensive_rebound_factor, n=1), k=5, align="right", fill=NA)
    ) %>% 
ungroup()

team_side <- rollingteamstats %>%
  select(
    game_id,
    team_id, 
    team_short_display_name, 
    opponent_team_id, 
    game_date, 
    season, 
    team_score, 
    team_rolling_ppp,
    team_rolling_median_value,
    team_rolling_fgpct,
    #team_cumulative_player_value,
    team_cumulative_ppp,
    offensive_rebounds,
    defensive_rebounds,
    team_rolling_fouls
    ) %>% 
  rename(
    team_offensive_rebounds = offensive_rebounds,
    team_defensive_rebounds = defensive_rebounds
  ) %>% 
  na.omit() 

opponent_side <- team_side %>%
  select(-opponent_team_id) %>% 
  rename(
    opponent_team_id = team_id,
    opponent_short_display_name = team_short_display_name,
    opponent_score = team_score,
    opponent_rolling_ppp = team_rolling_ppp,
    opponent_rolling_median_value = team_rolling_median_value,
    opponent_rolling_fgpct = team_rolling_fgpct,
    #opponent_cumulative_player_value = team_cumulative_player_value,
    opponent_cumulative_ppp = team_cumulative_ppp,
    opponent_offensive_rebounds = team_offensive_rebounds,
    opponent_defensive_rebounds = team_defensive_rebounds,
    opponent_rolling_fouls = team_rolling_fouls
  ) 

gameswithsides <- team_side %>% inner_join(opponent_side)

gameswithsides <- gameswithsides %>% mutate(
  team_result = as.factor(case_when(
    team_score > opponent_score ~ "W",
    opponent_score > team_score ~ "L"
  )),
team_offensive_rebound_factor = team_offensive_rebounds / (team_offensive_rebounds + opponent_defensive_rebounds),
opponent_offensive_rebound_factor = opponent_offensive_rebounds / (opponent_offensive_rebounds + team_defensive_rebounds),
team_rolling_offensive_rebound_factor = rollmean(team_offensive_rebound_factor, k=10, align="right", fill=NA),
opponent_rolling_offensive_rebound_factor = rollmean(opponent_offensive_rebound_factor, k=10, align="right", fill=NA
),
team_defensive_rebound_factor = team_defensive_rebounds / (team_defensive_rebounds + opponent_offensive_rebounds),
opponent_defensive_rebound_factor = opponent_defensive_rebounds / (opponent_defensive_rebounds + team_offensive_rebounds),
team_rolling_defensive_rebound_factor = rollmean(team_defensive_rebound_factor, k=10, align="right", fill=NA),
opponent_rolling_defensive_rebound_factor = rollmean(opponent_defensive_rebound_factor, k=10, align="right", fill=NA
) ) %>% 
na.omit()

levels(gameswithsides$team_result)

gameswithsides$team_result <- relevel(gameswithsides$team_result, ref="W")

levels(gameswithsides$team_result)

modelgames <- gameswithsides %>% 
  select(
    game_id, 
    game_date, 
    team_short_display_name, 
    opponent_short_display_name, 
    season, 
    team_rolling_ppp, 
    #opponent_rolling_ppp, 
    team_result,
    team_rolling_median_value,
    opponent_rolling_median_value,
    team_rolling_fgpct,
    opponent_rolling_fgpct,
    #team_cumulative_player_value,
    team_cumulative_ppp,
    #opponent_cumulative_player_value,
    #opponent_cumulative_ppp,
    team_rolling_offensive_rebound_factor,
    opponent_rolling_offensive_rebound_factor,
    #team_rolling_defensive_rebound_factor,
    #opponent_rolling_defensive_rebound_factor,
    team_rolling_fouls,
    opponent_rolling_fouls
    ) %>% na.omit()
```

----- PREDICTIONS -----
```{r}
playingames <- tibble(
  team_short_display_name="Texas A&M-CC",
  opponent_short_display_name="SE Missouri St"
) %>% add_row(
  team_short_display_name="Texas Southern",
  opponent_short_display_name="Fair Dickinson"
) %>% add_row(
  team_short_display_name="Mississippi St",
  opponent_short_display_name="Pitt"
) %>% add_row(
  team_short_display_name="Arizona St",
  opponent_short_display_name="Nevada"
) 
```

```{r}
playingames <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(playingames)

playingames <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(playingames) 

```

```{r}
playin <- lightgbm_fit %>% 
  predict(new_data = playingames) %>%
  bind_cols(playingames) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

playin <- lightgbm_fit %>% 
  predict(new_data = playingames, type="prob") %>%
  bind_cols(playin) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

playin
```

```{r}
southround1games <- tibble(
  team_short_display_name="Alabama",
  opponent_short_display_name="Texas A&M-CC"
) %>% add_row(
  team_short_display_name="Maryland",
  opponent_short_display_name="West Virginia"
) %>% add_row(
  team_short_display_name="San Diego St",
  opponent_short_display_name="Charleston"
) %>% add_row(
  team_short_display_name="Virginia",
  opponent_short_display_name="Furman"
) %>% add_row(
  team_short_display_name="Creighton",
  opponent_short_display_name="NC State"
) %>% add_row(
  team_short_display_name="Baylor",
  opponent_short_display_name="UCSB"
) %>% add_row(
  team_short_display_name="Missouri",
  opponent_short_display_name="Utah State"
) %>% add_row(
  team_short_display_name="Arizona",
  opponent_short_display_name="Princeton"
)
```

```{r}
southround1games <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(southround1games)

southround1games <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(southround1games) 

```

```{r}
southround1 <- lightgbm_fit %>% 
  predict(new_data = southround1games) %>%
  bind_cols(southround1games) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

southround1 <- lightgbm_fit %>% 
  predict(new_data = southround1games, type="prob") %>%
  bind_cols(southround1) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

southround1
```

-----

```{r}
southround2games <- tibble(
  team_short_display_name="Alabama",
  opponent_short_display_name="Maryland"
) %>% add_row(
  team_short_display_name="San Diego St",
  opponent_short_display_name="Virginia"
) %>% add_row(
  team_short_display_name="Creighton",
  opponent_short_display_name="Baylor"
) %>% add_row(
  team_short_display_name="Missouri",
  opponent_short_display_name="Arizona"
) 
```

```{r}
southround2games <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(southround2games)

southround2games <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(southround2games) 

```

```{r}
southround2 <- lightgbm_fit %>% 
  predict(new_data = southround2games) %>%
  bind_cols(southround2games) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

southround2 <- lightgbm_fit %>% 
  predict(new_data = southround2games, type="prob") %>%
  bind_cols(southround2) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

southround2
```

-----

```{r}
southround3games <- tibble(
  team_short_display_name="Alabama",
  opponent_short_display_name="Virginia"
) %>% add_row(
  team_short_display_name="Creighton",
  opponent_short_display_name="Missouri"
) 
```

```{r}
southround3games <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(southround3games)

southround3games <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(southround3games) 

```

```{r}
southround3 <- lightgbm_fit %>% 
  predict(new_data = southround3games) %>%
  bind_cols(southround3games) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

southround3 <- lightgbm_fit %>% 
  predict(new_data = southround3games, type="prob") %>%
  bind_cols(southround3) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

southround3
```

-----

```{r}
southround4games <- tibble(
  team_short_display_name="Alabama",
  opponent_short_display_name="Creighton"
) 
```

```{r}
southround4games <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(southround4games)

southround4games <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(southround4games) 

```

```{r}
southround4 <- lightgbm_fit %>% 
  predict(new_data = southround4games) %>%
  bind_cols(southround4games) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

southround4 <- lightgbm_fit %>% 
  predict(new_data = southround4games, type="prob") %>%
  bind_cols(southround4) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

southround4
```

-----

```{r}
eastround1games <- tibble(
  team_short_display_name="Purdue",
  opponent_short_display_name="Fair Dickinson"
) %>% add_row(
  team_short_display_name="Memphis",
  opponent_short_display_name="FAU"
) %>% add_row(
  team_short_display_name="Duke",
  opponent_short_display_name="Oral Roberts"
) %>% add_row(
  team_short_display_name="Tennessee",
  opponent_short_display_name="Louisiana"
) %>% add_row(
  team_short_display_name="Kentucky",
  opponent_short_display_name="Providence"
) %>% add_row(
  team_short_display_name="Kansas St",
  opponent_short_display_name="Montana St"
) %>% add_row(
  team_short_display_name="Michigan St",
  opponent_short_display_name="USC"
) %>% add_row(
  team_short_display_name="Marquette",
  opponent_short_display_name="Vermont"
) 
```

```{r}
eastround1games <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(eastround1games)

eastround1games <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(eastround1games) 

```

```{r}
eastround1 <- lightgbm_fit %>% 
  predict(new_data = eastround1games) %>%
  bind_cols(eastround1games) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

eastround1 <- lightgbm_fit %>% 
  predict(new_data = eastround1games, type="prob") %>%
  bind_cols(eastround1) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

eastround1
```

-----
```{r}
eastround2games <- tibble(
  team_short_display_name="Purdue",
  opponent_short_display_name="Memphis"
) %>% add_row(
  team_short_display_name="Duke",
  opponent_short_display_name="Louisiana"
) %>% add_row(
  team_short_display_name="Kentucky",
  opponent_short_display_name="Kansas St"
) %>% add_row(
  team_short_display_name="USC",
  opponent_short_display_name="Marquette"
)
```

```{r}
eastround2games <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(eastround2games)

eastround2games <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(eastround2games) 

```

```{r}
eastround2 <- lightgbm_fit %>% 
  predict(new_data = eastround2games) %>%
  bind_cols(eastround2games) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

eastround2 <- lightgbm_fit %>% 
  predict(new_data = eastround2games, type="prob") %>%
  bind_cols(eastround2) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

eastround2
```


```{r}
eastround3games <- tibble(
  team_short_display_name="Purdue",
  opponent_short_display_name="Duke"
) %>% add_row(
  team_short_display_name="Kentucky",
  opponent_short_display_name="Marquette"
)
```

```{r}
eastround3games <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(eastround3games)

eastround3games <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(eastround3games) 

```

```{r}
eastround3 <- lightgbm_fit %>% 
  predict(new_data = eastround3games) %>%
  bind_cols(eastround3games) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

eastround3 <- lightgbm_fit %>% 
  predict(new_data = eastround3games, type="prob") %>%
  bind_cols(eastround3) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

eastround3
```
----

```{r}
eastround4games <- tibble(
  team_short_display_name="Duke",
  opponent_short_display_name="Marquette"
)
```

```{r}
eastround4games <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(eastround4games)

eastround4games <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(eastround4games) 

```

```{r}
eastround4 <- lightgbm_fit %>% 
  predict(new_data = eastround4games) %>%
  bind_cols(eastround4games) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

eastround4 <- lightgbm_fit %>% 
  predict(new_data = eastround4games, type="prob") %>%
  bind_cols(eastround4) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

eastround4
```
-----

```{r}
midwestround1games <- tibble(
  team_short_display_name="Houston",
  opponent_short_display_name="N Kentucky"
) %>% add_row(
  team_short_display_name="Iowa",
  opponent_short_display_name="Auburn"
) %>% add_row(
  team_short_display_name="Miami",
  opponent_short_display_name="Drake"
) %>% add_row(
  team_short_display_name="Indiana",
  opponent_short_display_name="Kent State"
) %>% add_row(
  team_short_display_name="Iowa State",
  opponent_short_display_name="Mississippi St"
) %>% add_row(
  team_short_display_name="Xavier",
  opponent_short_display_name="Kennesaw St"
) %>% add_row(
  team_short_display_name="Texas A&M",
  opponent_short_display_name="Penn State"
) %>% add_row(
  team_short_display_name="Texas",
  opponent_short_display_name="Colgate"
)
```

```{r}
midwestround1games <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(midwestround1games)

midwestround1games <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(midwestround1games) 

```

```{r}
midwestround1 <- lightgbm_fit %>% 
  predict(new_data = midwestround1games) %>%
  bind_cols(midwestround1games) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

midwestround1 <- lightgbm_fit %>% 
  predict(new_data = midwestround1games, type="prob") %>%
  bind_cols(midwestround1) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

midwestround1
```

----

```{r}
midwestround2games <- tibble(
  team_short_display_name="Houston",
  opponent_short_display_name="Iowa"
) %>% add_row(
  team_short_display_name="Miami",
  opponent_short_display_name="Indiana"
) %>% add_row(
  team_short_display_name="Iowa State",
  opponent_short_display_name="Xavier"
) %>% add_row(
  team_short_display_name="Texas A&M",
  opponent_short_display_name="Colgate"
)
```

```{r}
midwestround2games <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(midwestround2games)

midwestround2games <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(midwestround2games) 

```

```{r}
midwestround2 <- lightgbm_fit %>% 
  predict(new_data = midwestround2games) %>%
  bind_cols(midwestround2games) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

midwestround2 <- lightgbm_fit %>% 
  predict(new_data = midwestround2games, type="prob") %>%
  bind_cols(midwestround2) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

midwestround2
```

-----

```{r}
midwestround3games <- tibble(
  team_short_display_name="Houston",
  opponent_short_display_name="Miami"
) %>% add_row(
  team_short_display_name="Xavier",
  opponent_short_display_name="Texas A&M"
) 
```

```{r}
midwestround3games <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(midwestround3games)

midwestround3games <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(midwestround3games) 

```

```{r}
midwestround3 <- lightgbm_fit %>% 
  predict(new_data = midwestround3games) %>%
  bind_cols(midwestround3games) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

midwestround3 <- lightgbm_fit %>% 
  predict(new_data = midwestround3games, type="prob") %>%
  bind_cols(midwestround3) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

midwestround3
```

----

```{r}
midwestround4games <- tibble(
  team_short_display_name="Houston",
  opponent_short_display_name="Xavier"
) 
```

```{r}
midwestround4games <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(midwestround4games)

midwestround4games <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(midwestround4games) 

```

```{r}
midwestround4 <- lightgbm_fit %>% 
  predict(new_data = midwestround4games) %>%
  bind_cols(midwestround4games) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

midwestround4 <- lightgbm_fit %>% 
  predict(new_data = midwestround4games, type="prob") %>%
  bind_cols(midwestround4) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

midwestround4
```

-----
```{r}
westround1games <- tibble(
  team_short_display_name="Kansas",
  opponent_short_display_name="Howard"
) %>% add_row(
  team_short_display_name="Arkansas",
  opponent_short_display_name="Illinois"
) %>% add_row(
  team_short_display_name="Saint Mary's",
  opponent_short_display_name="VCU"
) %>% add_row(
  team_short_display_name="UConn",
  opponent_short_display_name="Iona"
) %>% add_row(
  team_short_display_name="TCU",
  opponent_short_display_name="Nevada"
) %>% add_row(
  team_short_display_name="Gonzaga",
  opponent_short_display_name="Grand Canyon"
) %>% add_row(
  team_short_display_name="Northwestern",
  opponent_short_display_name="Boise St"
) %>% add_row(
  team_short_display_name="UCLA",
  opponent_short_display_name="UNC Asheville"
) 
```

```{r}
westround1games <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(westround1games)

westround1games <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(westround1games) 

```

```{r}
westround1 <- lightgbm_fit %>% 
  predict(new_data = westround1games) %>%
  bind_cols(westround1games) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

westround1 <- lightgbm_fit %>% 
  predict(new_data = westround1games, type="prob") %>%
  bind_cols(westround1) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

westround1
```

-----
```{r}
westround2games <- tibble(
  team_short_display_name="Kansas",
  opponent_short_display_name="Arkansas"
) %>% add_row(
  team_short_display_name="Saint Mary's",
  opponent_short_display_name="UConn"
) %>% add_row(
  team_short_display_name="TCU",
  opponent_short_display_name="Gonzaga"
) %>% add_row(
  team_short_display_name="Boise St",
  opponent_short_display_name="UNC Asheville"
) 
```

```{r}
westround2games <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(westround2games)

westround2games <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(westround2games) 

```

```{r}
westround2 <- lightgbm_fit %>% 
  predict(new_data = westround2games) %>%
  bind_cols(westround2games) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

westround2 <- lightgbm_fit %>% 
  predict(new_data = westround2games, type="prob") %>%
  bind_cols(westround2) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

westround2
```

-----
```{r}
westround3games <- tibble(
  team_short_display_name="Kansas",
  opponent_short_display_name="Saint Mary's"
) %>% add_row(
  team_short_display_name="Gonzaga",
  opponent_short_display_name="Boise St"
) 
```

```{r}
westround3games <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(westround3games)

westround3games <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(westround3games) 

```

```{r}
westround3 <- lightgbm_fit %>% 
  predict(new_data = westround3games) %>%
  bind_cols(westround3games) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

westround3 <- lightgbm_fit %>% 
  predict(new_data = westround3games, type="prob") %>%
  bind_cols(westround3) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

westround3
```

-----
```{r}
westround4games <- tibble(
  team_short_display_name="Kansas",
  opponent_short_display_name="Gonzaga"
) 
```

```{r}
westround4games <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(westround4games)

westround4games <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(westround4games) 

```

```{r}
westround4 <- lightgbm_fit %>% 
  predict(new_data = westround4games) %>%
  bind_cols(westround4games) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

westround4 <- lightgbm_fit %>% 
  predict(new_data = westround4games, type="prob") %>%
  bind_cols(westround4) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

westround4
```

----

```{r}
finalfourgames <- tibble(
  team_short_display_name="Alabama",
  opponent_short_display_name="Marquette"
) %>% add_row(
  team_short_display_name="Houston",
  opponent_short_display_name="Gonzaga"
) 
```

```{r}
finalfourgames <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(finalfourgames)

finalfourgames <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(finalfourgames) 

```

```{r}
finalfour <- lightgbm_fit %>% 
  predict(new_data = finalfourgames) %>%
  bind_cols(finalfourgames) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

finalfour <- lightgbm_fit %>% 
  predict(new_data = finalfourgames, type="prob") %>%
  bind_cols(finalfour) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

finalfour
```

----

```{r}
championshipgames <- tibble(
  team_short_display_name="Marquette",
  opponent_short_display_name="Houston"
)
```

```{r}
championshipgames <- modelgames %>% 
  group_by(team_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  select(-team_result, -starts_with("opponent")) %>% 
  right_join(championshipgames)

championshipgames <- modelgames %>% 
  group_by(opponent_short_display_name) %>% 
  filter(game_date == max(game_date) & season == 2023) %>% 
  slice(1) %>% 
  ungroup() %>% 
  select(-team_result, -starts_with("team"), -game_id, -game_date, -season) %>% right_join(championshipgames) 

```

```{r}
championship <- lightgbm_fit %>% 
  predict(new_data = championshipgames) %>%
  bind_cols(championshipgames) %>% 
  select(.pred_class, team_short_display_name, opponent_short_display_name, everything())

championship <- lightgbm_fit %>% 
  predict(new_data = championshipgames, type="prob") %>%
  bind_cols(championship) %>% 
  select(.pred_class, .pred_W, .pred_L, team_short_display_name, opponent_short_display_name, everything())

championship
```

Go Marquette!!



